---
title: "Live Session 2 Assignment 403"
author: "Mike Martos"
date: "May 18, 2016"
output: 
  html_document :
    keep_md : true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Calculation Questions (using R)
##1.	Basic Math

###a.	The log of a positive number
```{r Log}
log(10)
```
###b.	What is the default base for the log function? Calculate the log of your previous number with a different base.
Natural Logarithm

###c.	The log of a negative number 
NaN not possible to take the log of a negative number

###d.	The square-root of a positive number
```{r Sqrt}
sqrt(81)
```

 
##2.	Random number generation.

###a.	Create a vector of 15 standard normal random variables. Calculate its mean and SD.
```{r  rnorm(15)}
vec <- rnorm(15)
sd(vec)
mean(vec)
```

 
###b.	Change the mean to 10 and the SD to 2 and recalculate the vector of 15 random normal variables. Calculate its mean and SD.
```{r rnorm}
rnorm(15, mean = 10, sd = 2)
vec_10_2 <- rnorm(15,10,2)
sd(vec_10_2)
mean(vec_10_2)
```

 
###c.	Why are the means and SD not exactly the same as the means and SDs specified in the function?
Because it is random and the more samples the closer the mean and SD will be to the defined values in the function

##3.	 Vector Operations

###a.	The weights of 6 individuals in kg are 60, 72, 57, 90, 95, 72
###b.	Their heights (in m) are 1.80, 1.85, 1.72, 1.90, 1.74, 1.91
###c.	Enter these vectors into R
```{r Create Vectors}
weight <- c(60, 72, 57, 90, 95, 72)
height <- c(1.80, 1.85, 1.72, 1.90, 1.74, 1.91)
```


###d.	Create a scatterplot of weight vs. height. Interpret the scatterplot.
```{r Scatterplot}
plot(weight, height, main="Scatterplot Example", xlab="Weights", ylab="Heights")
```

 
The points seem disperse but there is a positive relationship between weight and height.
 
###e.	Calculate the BMI for each individual (BMI = weight in kg divided by the square of the height in m)
```{r bmi}
bmi <- (weight/height^2)
print(bmi)
```

 
###f.	Calculate the mean for weight
```{r mean Weight}
mean(weight)
```


###g.	Subtract the mean from each value of weight
```{r Weight difference}
wm <- (weight-mean(weight))
print(wm)
```

 
###h.	Sum the result. Now you know why we square the deviations from the mean to calculate a standard deviation!
```{r Sum Weight differendce}
sum(wm)
```
Very small number (0)



